Structural controllability of ecological networks

### 2018-06-19 paper/reviewers-response.Rmd

---
title: "Ecological network control"
subtitle: "JEcol-2017-0720 - Detailed response to comments"
author: "Fernando Cagua, Kate L. Wootton, Daniel B. Stouffer"
classoption: a4paper
csl: journal-of-ecology.csl
documentclass: artikel1
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    toc: false
    number_sections: false
header-includes:
  - \usepackage{setspace}
  - \usepackage{xr}
  - \usepackage{lineno}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument[M-]{manuscript}
  - \externaldocument[S-]{supp-info}
  - \usepackage[most]{tcolorbox}
  - \definecolor{block-gray}{gray}{0.9}
  - \newtcolorbox{myquote}{colback=block-gray,grow to right by=-10mm,grow to left by=-10mm, boxrule=0pt,boxsep=0pt,breakable}
---

### 2018-06-19 paper/manuscript.Rmd
Add capability to reference lines

---
title: "Structural controllability of ecological networks"
classoption: a4paper
csl: journal-of-ecology.csl
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    number_sections: false
toc: false
header-includes:
- \usepackage{geometry}
# - \geometry{right=3in,marginparwidth=2.5in}
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{caption}
- \usepackage{lineno}
- \usepackage{xr}
- \externaldocument[S-]{supp-info}
- \usepackage{siunitx}
- \usepackage{multirow}
- \usepackage{makecell}
- \usepackage{threeparttablex}
documentclass: artikel1
bibliography: phd-bibliography/network-control.bib
---

@@

Just like the centrality metrics, the information obtained by applying structural controllability depends on the ability of the network to accurately represent the ecological community. 
We tested the sensitivity of our approach to two fundamental assumptions. 
First, we tested that visitation is an appropriate proxy to infer interspecific effects. 
To do that we compared the results obtained using visitation to two alternative metrics in a dataset that lacked invasive species [@ballantyne_constructing_2015]. 
Specifically, we also applied the structural controllability approach to networks constructed using pollinator efficiency (which measures the pollen deposition of an interaction) and pollinator importance (which accounts for both pollen deposition and visitation and hence is regarded as a more accurate estimation of the pollination service received by plants) [@neeman_framework_2009]. More details in the Supporting Information Section \@ref(S-visitation-as-proxy). 
Second, because interspecific dependencies depend on the network topology and consequently on the accurate sampling of interactions, we tested the robustness of structural controllability to the undersampling of interactions. 
To do that we compared the results obtained when using the full network and when randomly removing interactions preferentially from the weakest links in the network. 
This effectively removed the rare interactions from the networks (more details in the Supporting Information Section \@ref(S-undersampling)).

@@

We found that using visitation as a proxy for the strength of species interactions leads to similar results than those obtained using pollinator importance [regarded as an accurate measure of the pollination service to plants; Supporting Information Section \@ref(S-visitation-as-proxy); @neeman_framework_2009]. 
Importantly, we also found that structural stability is robust to incomplete sampling of interactions. 
We found a very strong agreement between results obtained using the complete empirical networks and those obtained by randomly removing interactions (Supporting Information Section \@ref(S-undersampling)). 
Despite removing rare interactions and species, the relative size of the minimum driver node-set, the superior species, and the relative rankings of control capacity were generally maintained. Remarkably critical species in the full network were also critical in the vast majority of rarefied networks.

>>>>

---
title: "Structural controllability of ecological networks"
classoption: a4paper
csl: journal-of-ecology.csl
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    number_sections: false
toc: false
header-includes:
- \usepackage{geometry}
# - \geometry{right=3in,marginparwidth=2.5in}
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{caption}
- \usepackage{lineno}
- \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
- \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
- \usepackage{xr}
- \externaldocument[S-]{supp-info}
- \usepackage{siunitx}
- \usepackage{multirow}
- \usepackage{makecell}
- \usepackage{threeparttablex}
documentclass: artikel1
bibliography: phd-bibliography/network-control.bib
---

@@

\R{testing-assumptions-line}Just like the centrality metrics, the information obtained by applying structural controllability depends on the ability of the network to accurately represent the ecological community. 
We tested the sensitivity of our approach to two fundamental assumptions. 
First, we tested that visitation is an appropriate proxy to infer interspecific effects. 
To do that we compared the results obtained using visitation to two alternative metrics in a dataset that lacked invasive species [@ballantyne_constructing_2015]. 
Specifically, we also applied the structural controllability approach to networks constructed using pollinator efficiency (which measures the pollen deposition of an interaction) and pollinator importance (which accounts for both pollen deposition and visitation and hence is regarded as a more accurate estimation of the pollination service received by plants) [@neeman_framework_2009]. More details in the Supporting Information Section \@ref(S-visitation-as-proxy). 
Second, because interspecific dependencies depend on the network topology and consequently on the accurate sampling of interactions, we tested the robustness of structural controllability to the undersampling of interactions. 
To do that we compared the results obtained when using the full network and when randomly removing interactions preferentially from the weakest links in the network. 
This effectively removed the rare interactions from the networks (more details in the Supporting Information Section \@ref(S-undersampling)).

@@

\R{testing-asumptions-results-line} We found that using visitation as a proxy for the strength of species interactions leads to similar results than those obtained using pollinator importance [regarded as an accurate measure of the pollination service to plants; Supporting Information Section \@ref(S-visitation-as-proxy); @neeman_framework_2009]. 
Importantly, we also found that structural stability is robust to incomplete sampling of interactions. 
We found a very strong agreement between results obtained using the complete empirical networks and those obtained by randomly removing interactions (Supporting Information Section \@ref(S-undersampling)). 
Despite removing rare interactions and species, the relative size of the minimum driver node-set, the superior species, and the relative rankings of control capacity were generally maintained. Remarkably critical species in the full network were also critical in the vast majority of rarefied networks.
